Boundary Labeling for annotated documents

### 2018-06-10 LaTeX/Paper.tex
Paper: Style and presentation changes. Program: No changes.

%TODO: Abstract: \begin{abstract}...\end{abstract}

@@

\section{GUI}
\label{sec:GUI}
The GUI of the program is kept simple, as the main goal was to demonstrate the routing algorithm. All customization options are located on the control panel above the drawing area, which contains the text, leaders and annotations. (See also Fig.~\ref*{fig:ProgWindow})

@@

If any of the parameters on the control panel (see section~\ref*{sec:GUI}) are changed, the process re-starts from the beginning.

@@

To generate data, we created our own texts using word length statistics from Table III in "Length-frequency statistics for written English" by Miller et al. \cite{Miller1958}, which lists word frequencies by length. We opted to use the data from the "Content Words" column, as the combined statistics almost exclusively produced words with three or less letters in our tests. \change{Furthermore, we created a custom distribution based on these values to test the algorithm's behavior in texts with longer words.}
Using this data, we compiled our own fixed-length testing texts by creating words containing randomized alphabetic characters, taking care that the word length distribution matched our data. \change{The results of both distributions can be seen in Fig.~\ref{fig:wordlength}}
A fixed number of annotation sites is inserted into the text either by distributing their locations uniformly across the text, or by clustering them regionally.

@@

Across every test run, the first two instances always took significantly longer to complete than subsequent ones. As this was replicated even when using the same text for all 100 passes, we believe this to be an issue caused by the implementation rather than the algorithm itself. 
\change{Another issue was a significantly increased execution time for some instances, which could not be reproduced in subsequent tests under the same conditions and are assumed to be caused by differences in scheduling or Java's garbage collection. Disregarding these outliers, the worst time measured across all tests was about two milliseconds.}%Wie kann ich sagen, dass der Computer heiß läuft?

@@

 \begin{figure}
 	\centering
 	\begin{subfigure}[b]{\textwidth}
 		\centering
 		\includegraphics[scale=0.6]{Rplot_10u.png}
 		\caption{\label{fig:10u}Results for 10 sources}
 	\end{subfigure}

 	\begin{subfigure}[b]{\textwidth}
 		\centering
 		\includegraphics[scale=0.6]{Rplot_15u.png}
 		\caption{\label{fig:15u}Results for 15 sources}
 	\end{subfigure}
    \begin{subfigure}[b]{\textwidth}
		 \centering
		 \includegraphics[scale=0.6]{Rplot_30u.png}
		 \caption{\label{fig:30u}Results for 30 sources}
    \end{subfigure}

 	\caption{Three plots of test batches with identical seeds. \change{Each instance used a uniform distribution of sources and a 300-word text.}}
 	\label{fig:uniformstats}
 \end{figure}

@@

\newpage
\change{Re-running the tests with an increased word length showed several changes: Most noticable was a higher variance in results - whereas the histogram in Fig.~\ref*{fig:15u} has a noticable peak at 10 successful routings, the values in Fig.~\ref*{fig:15uLong} are more spread out, reaching both better and worse end results.
The bottom left clustering also no longer achieves obviously better results than other vertex placements. While Fig.~\ref*{fig:15blLong} has less results with nine or less successful routings then Fig.~\ref*{fig:15uLong}, it also has less results in the 12+ range.
Finally, the vertical placement of vertices has a noticable impact - Fig.~\ref*{fig:15blLong} contains less results in below 10 successful routings than Fig.~\ref*{fig:15brLong}, and even has some instances with 13 successes.}

\begin{figure}
	\centering
	\begin{subfigure}[b]{\textwidth}
		\centering
		\includegraphics[scale=0.6]{Rplot_15u_longer.png}
		\caption{\label{fig:15uLong}Results for uniform distribution.}
	\end{subfigure}
	\begin{subfigure}[b]{\textwidth}
		\centering
		\includegraphics[scale=0.6]{Rplot_15bl_longer.png}
		\caption{\label{fig:15blLong}Results for clustered distribution in the bottom left.}
	\end{subfigure}
	\begin{subfigure}[b]{\textwidth}
		\centering
		\includegraphics[scale=0.6]{Rplot_15br_longer.png}
		\caption{\label{fig:15brLong}Results for clustered distribution in the bottom right.}
	\end{subfigure}
	\caption{Test results for instances with 15 differently distributed sources over a 300-word text with increased word length.}
	\label{fig:longTests}
\end{figure}
%Increasing the word length would make this effect more severe, and it would be interesting to see the influence on the results.

@@

\change{In this paper we presented an algorithm capable of solving the one-sided boundary labeling problem for monotonous, crossing-free OPO-Leaders using only the whitespace between words and lines. We have shown it to run in $O(n^2)$ and proven its correctness. Finally, we have evaluated its performance under different conditions.}

\section{Further notes}

\change{An obvious weakness of our algorithm is its inability to create routings for source nodes above the next free annotation positions. Adding leaders that are only allowed to go down instead of up would allow for these positions to be routed, but would require extra precautions to avoid intersecting leaders. Alternatively, leaders could be restricted by how many P-Segments can be included before reaching the labeling area to make them easier to follow.}

>>>>

@@

\section{User Interface}
\label{sec:UI}
The GUI of the program is kept simple, as the main goal was to demonstrate the routing algorithm. All customization options are located on the control panel above the drawing area, which contains the text, leaders and annotations. (See also Fig.~\ref*{fig:ProgWindow})

@@

If any of the parameters on the control panel (see section~\ref*{sec:UI}) are changed, the process re-starts from the beginning.

@@

To generate data, we created our own texts using word length statistics from Table III in "Length-frequency statistics for written English" by Miller et al. \cite{Miller1958}, which lists word frequencies by length. We opted to use the data from the "Content Words" column, as the combined statistics almost exclusively produced words with three or less letters in our tests. Furthermore, we created a custom distribution based on these values to test the algorithm's behavior in texts with longer words.
Using this data, we compiled our own fixed-length testing texts by creating words containing randomized alphabetic characters, taking care that the word length distribution matched our data. The results of both distributions can be seen in Fig.~\ref{fig:wordlength}
A fixed number of annotation sites is inserted into the text either by distributing their locations uniformly across the text, or by clustering them regionally.

@@

Across every test run, the first two instances always took significantly longer to complete than subsequent ones. As this was replicated even when using the same text for all 100 passes, we believe this to be an issue caused by the implementation rather than the algorithm itself. 
Another issue was a significantly increased execution time for some instances, which could not be reproduced in subsequent tests under the same conditions and are assumed to be caused by differences in scheduling or Java's garbage collection. Disregarding these outliers, the worst time measured across all tests was about two milliseconds.%Wie kann ich sagen, dass der Computer heiß läuft?

@@

 \begin{figure}
 	\centering
 	\begin{subfigure}[b]{\textwidth*2/7}
 		\centering
 		\includegraphics[scale=0.35]{Rplot_10u.png}
 		\caption{\label{fig:10u}Results for 10 sources}
 	\end{subfigure}
 	\begin{subfigure}[b]{\textwidth*2/7}
 		\centering
 		\includegraphics[scale=0.35]{Rplot_15u.png}
 		\caption{\label{fig:15u}Results for 15 sources}
 	\end{subfigure}
    \begin{subfigure}[b]{\textwidth*2/7}
		 \centering
		 \includegraphics[scale=0.35]{Rplot_30u.png}
		 \caption{\label{fig:30u}Results for 30 sources}
    \end{subfigure}

 	\caption{Three plots of test batches with identical seeds. Each instance used a uniform distribution of sources and a 300-word text.}
 	\label{fig:uniformstats}
 \end{figure}

@@

Re-running the tests with an increased word length showed several changes: Most noticable was a higher variance in results - whereas the histogram in Fig.~\ref*{fig:15u} has a noticable peak at 10 successful routings, the values in Fig.~\ref*{fig:15uLong} are more spread out, reaching both better and worse end results.
The bottom left clustering also no longer achieves obviously better results than other vertex placements. While Fig.~\ref*{fig:15blLong} has less results with nine or less successful routings then Fig.~\ref*{fig:15uLong}, it also has less results in the 12+ range.
Finally, the vertical placement of vertices has a noticable impact - Fig.~\ref*{fig:15blLong} contains less results in below 10 successful routings than Fig.~\ref*{fig:15brLong}, and even has some instances with 13 successes.

\begin{figure}
	\centering
	\begin{subfigure}[b]{\textwidth*5/11}
		\centering
		\includegraphics[scale=0.55]{Rplot_15u_longer.png}
		\caption{\label{fig:15uLong}Results for uniform distribution.}
	\end{subfigure}

	\begin{subfigure}[b]{\textwidth*5/11}
		\centering
		\includegraphics[scale=0.55]{Rplot_15bl_longer.png}
		\caption{\label{fig:15blLong}Results for clustered distribution in the bottom left.}
	\end{subfigure}~~%This is here to increase the space between the figures
	\begin{subfigure}[b]{\textwidth*5/11}
		\centering
		\includegraphics[scale=0.55]{Rplot_15br_longer.png}
		\caption{\label{fig:15brLong}Results for clustered distribution in the bottom right.}
	\end{subfigure}
	\caption{Test results for instances with 15 differently distributed sources over a 300-word text with increased word length.}
	\label{fig:longTests}
\end{figure}
%Increasing the word length would make this effect more severe, and it would be interesting to see the influence on the results.

@@

In this paper we presented an algorithm capable of solving the one-sided boundary labeling problem for monotonous, crossing-free OPO-Leaders using only the whitespace between words and lines. We have shown it to run in $O(n^2)$ and proven its correctness. Finally, we have evaluated its performance under different conditions.

An obvious weakness of our algorithm is its inability to create routings for source nodes above the next free annotation positions. Adding leaders that are only allowed to go down instead of up would allow for these positions to be routed, but would require extra precautions to avoid intersecting leaders. Alternatively, leaders could be restricted by how many P-Segments can be included before reaching the labeling area to make them easier to follow.
